\hspace{25cm}Debiased Calibration for Generalized Two-Phase Sampling

### 2024-08-02 final/jsm_poster.tex
Updated JSM poster size. Submitted final to print.

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[size=custom,width=120,height=72,scale=1.0]{beamerposter}
\usetheme{gemini}
\usecolortheme{gemini}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{bm}
\pgfplotsset{compat=1.14}
\usepackage{anyfontsize}
\usepackage[backend=biber, style=bwl-FU]{biblatex}
\addbibresource{poster.bib}

@@

\title{\hspace{25cm}Debiased Calibration for Generalized Two-Phase Sampling}

@@

\begin{document}
\addtobeamertemplate{headline}{}
{
    \begin{tikzpicture}[remember picture,overlay]
        \node [anchor=north west, inner sep=3cm] at ([xshift=0.0cm,yshift=1.0cm]current page.north west){\includegraphics[height=2.5cm]{logos/watermark.png}}; % Iowa State University watermark
        % ISU watermark can be found on https://www.brandmarketing.iastate.edu/wordmark/primary/
        \node [anchor=north west, inner sep=3cm] at ([xshift=0.0cm,yshift=-2.5cm]current page.north west){\huge \textbf{Statistics Department}}; % Department name
        %\node [anchor=north east, inner sep=3cm] at ([xshift=0.0cm,yshift=1.0cm]current page.north east){\includegraphics[height=5cm]{logos/logo.png}}; % Use this if you want to add a logo on your right top corner.
    \end{tikzpicture}
}

@@

    In classical two-phase sampling, one first selects a sample $A_1$ from a
    finite population $U$ of size $N$, and observes $({\bf X}_i)_{i = 1}^{n_1}$.
    Then one selects a sample $A_2$ from $A_1$ and observes 
    $({\bf X}_i, Y_i)_{i = 1}^{n_2}$. We take the
    framework of two-phase sampling and view data integration as specific case
    of observing a variable of interest $Y$ within a single data set while we
    also observe common covariates $({\bf X}_i)$ between both the data set with
    $Y$ as well as an outside auxilary sample. This is an important practical
    problem \cite{yang2020statistical}, 
    \cite{dagdoug2023model}. We focus on the case:

@@

    \heading{Notation}

@@

  \begin{block}{Goal}

@@

  % NOTE: Use the "alertblock" to highlight a particular section in green.
  \begin{block}{Comparable Methods}

@@

        where $q_i = q(\bf x_i)$ and

@@

    \begin{itemize}
      \item In a seminal paper, \cite{deville1992calibration} generalized the
        regression estimator to other loss functions besides squared-error loss
        for a sample $A$ with auxilary information about $X$. Their generalized
        loss function minimizes,

@@

    \begin{itemize}
      \item Recently, \cite{kwon2024debiased} proposed a calibration estimator that
        uses a generalized entropy function $G(w)$ (\cite{gneiting2007strictly})
        instead of the generalized loss function $G(w, d)$ of
        \cite{deville1992calibration}. They separate the bias calibration from
        the minimization term and solve the following equation for estimated
        sample weights:

        $$
        \hat w_{i} = \argmin_{w} \sum_{i \in A} G(w_i)
        \suchthat \sum_{i \in A} w_{i} {\bf{x}}_i = 
        \sum_{i \in U} {\bf{z}}_i,
        \sum_{i \in A} w_i g(d_i) = \sum_{i \in U} g(d_i) .
        $$

@@

  %\begin{theorem}[Design Consistency]\label{thm:dc1}
    Let $\bm \lambda^*$ be the probability limit of $\hat{\bm \lambda}$,
    where $\hat{\bm \lambda}$ are the corresponding Lagrange multipliers from
    Equation~\ref{eq:wmin}.
    Under some regularity conditions, $\bm \lambda^* = ({\bf 0}^T, 1)^T$ and

    $$\hat Y_{\rm{DCE}} = \hat Y_\ell(\bm \lambda^*, \bm \phi^*) + O_p(N / n_2)$$

    where
    \vspace{-1.3cm}

    $$\hat Y_{\ell}(\bm \lambda^*, \bm \phi^*) = \hat Y_{\rm{DEE}}+ 
    \left(\sum_{i \in A_1} d_{1i} {\bf z}_i q_i - \sum_{i \in A_2} d_{1i} 
    \pi_{2i \mid 1}^{-1}  {\bf z}_i q_i\right)\bm \phi^*$$

    \vspace{-1.3cm}
    and
    \vspace{-0.3cm}

    $$
    \bm \phi^* = 
    \left[\sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i {\bf z}_i^T q_i}{g'(d_{2i|1})}\right]^{-1}
    \sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i y_i}{g'(d_{2i|1})}.
    $$

@@

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[size=custom,width=96,height=72,scale=1.0]{beamerposter}
\usetheme{gemini}
\usecolortheme{gemini}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{bm, ulem}
\pgfplotsset{compat=1.14}
\usepackage{anyfontsize}
\usepackage[backend=biber, style=bwl-FU]{biblatex}
\addbibresource{poster.bib}

@@

\title{\hspace{32cm}Debiased Calibration for Generalized Two-Phase Sampling}

@@

\begin{document}
\addtobeamertemplate{headline}{}
{
    \begin{tikzpicture}[remember picture,overlay]
        \node [anchor=north west, inner sep=3cm] at ([xshift=0.0cm,yshift=1.0cm]current page.north west){\includegraphics[height=2.0cm]{logos/watermark.png}}; % Iowa State University watermark
        % ISU watermark can be found on https://www.brandmarketing.iastate.edu/wordmark/primary/
        \node [anchor=north west, inner sep=3cm] at ([xshift=0.0cm,yshift=-2.5cm]current page.north west){\huge \textbf{Statistics Department}}; % Department name
        %\node [anchor=north east, inner sep=3cm] at ([xshift=0.0cm,yshift=1.0cm]current page.north east){\includegraphics[height=5cm]{logos/logo.png}}; % Use this if you want to add a logo on your right top corner.
    \end{tikzpicture}
}

@@

    In classical two-phase sampling, one first selects a sample $A_1$ from a
    finite population $U$ of size $N$, and observes $({\bf X}_i)_{i = 1}^{n_1}$.
    Then one selects a sample $A_2$ from $A_1$ and observes 
    $({\bf X}_i, Y_i)_{i = 1}^{n_2}$. We take the
    framework of two-phase sampling and view data integration as specific case
    of observing a variable of interest $Y$ within a single data set while we
    also observe common covariates $({\bf X}_i)$ between both the data set with
    $Y$ as well as an outside auxiliary sample. 
    %\sout{This is an important practical problem \cite{yang2020statistical}, 
    %\cite{dagdoug2023model}.} 
    We focus on the case:

@@

    \vspace{-0.3cm}
    \heading{Notation}

@@

  \vspace{-0.7cm}
  \begin{block}{Goal}

@@

  % NOTE: Use the "alertblock" to highlight a particular section in green.
  \vspace{-0.7cm}
  \begin{block}{Comparable Methods}

@@

        where $q_i = q(\bf x_i)$ and 
        \vspace{-0.5cm}

@@

    \vspace{-0.3cm}
    \begin{itemize}
      \item In a seminal paper, \cite{deville1992calibration} generalized the
        regression estimator to other loss functions besides squared-error loss
        for a sample $A$ with auxiliary information about $X$. Their generalized
        loss function minimizes,

@@

    \vspace{-0.3cm}
    \begin{itemize}
      \item Recently, \cite{kwon2024debiased} proposed a calibration estimator that
        uses a generalized entropy function $G(w)$ (\cite{gneiting2007strictly})
        instead of the generalized loss function $G(w, d)$ of
        \cite{deville1992calibration}. They separate the bias calibration from
        the minimization term and solve the following equation for estimated
        sample weights:

        $$
        \hat w_{i} = \argmin_{w} \sum_{i \in A} G(w_i)
        \suchthat \sum_{i \in A} w_{i} {\bf{x}}_i = 
        \sum_{i \in U} {\bf{x}}_i,
        \sum_{i \in A} w_i g(d_i) = \sum_{i \in U} g(d_i) .
        $$

@@

  %\begin{theorem}[Design Consistency]\label{thm:dc1}
    %\sout{Let $\bm \lambda^*$ be the probability limit of $\hat{\bm \lambda}$,
    %where $\hat{\bm \lambda}$ are the corresponding Lagrange multipliers from
    %Equation~\ref{eq:wmin}.}
    Under some regularity conditions, %\sout{$\bm \lambda^* = ({\bf 0}^T, 1)^T$} and
    \vspace{-0.7cm}

    $$\hat Y_{\rm{DCE}} = \hat Y_\ell + O_p(N / n_2), $$

    \vspace{-1.0cm}
    where 
    \vspace{-1.3cm}

    $$\hat Y_{\ell} = \hat Y_{\rm{DEE}}+ 
    \left(\sum_{i \in A_1} d_{1i} {\bf z}_i - \sum_{i \in A_2} d_{1i} 
    \pi_{2i \mid 1}^{-1}  {\bf z}_i \right)\bm \phi^*$$

    \vspace{-1.3cm}
    and
    \vspace{-0.7cm}

    $$
    \bm \phi^* = 
    \left[\sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i {\bf z}_i^T}{g'(d_{2i|1})}\right]^{-1}
    \sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i y_i}{g'(d_{2i|1})}.
    $$

@@

  %\vspace{-1.0cm}

### 2024-08-02 final/jsm_poster_ov.tex
Updated JSM poster size. Submitted final to print.

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[size=custom,width=120,height=72,scale=1.0]{beamerposter}
\usetheme{gemini}
\usecolortheme{gemini}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{bm}
\pgfplotsset{compat=1.14}
\usepackage{anyfontsize}
\usepackage[backend=biber, style=bwl-FU]{biblatex}
\addbibresource{poster.bib}

@@

    In classical two-phase sampling, one first selects a sample $A_1$ from a
    finite population $U$ of size $N$, and observes $({\bf X}_i)_{i = 1}^{n_1}$.
    Then one selects a sample $A_2$ from $A_1$ and observes 
    $({\bf X}_i, Y_i)_{i = 1}^{n_2}$. We take the
    framework of two-phase sampling and view data integration as specific case
    of observing a variable of interest $Y$ within a single data set while we
    also observe common covariates $({\bf X}_i)$ between both the data set with
    $Y$ as well as an outside auxilary sample. This is an important practical
    problem \cite{yang2020statistical}, 
    \cite{dagdoug2023model}. We focus on the case:

@@

    \begin{itemize}
      \item In a seminal paper, \cite{deville1992calibration} generalized the
        regression estimator to other loss functions besides squared-error loss
        for a sample $A$ with auxilary information about $X$. Their generalized
        loss function minimizes,

@@

  %\begin{theorem}[Design Consistency]\label{thm:dc1}
    Let $\bm \lambda^*$ be the probability limit of $\hat{\bm \lambda}$,
    where $\hat{\bm \lambda}$ are the corresponding Lagrange multipliers from
    Equation~\ref{eq:wmin}.
    Under some regularity conditions, $\bm \lambda^* = ({\bf 0}^T, 1)^T$ and

    $$\hat Y_{\rm{DCE}} = \hat Y_\ell(\bm \lambda^*, \bm \phi^*) + O_p(N / n_2)$$

@@

    $$\hat Y_{\ell}(\bm \lambda^*, \bm \phi^*) = \hat Y_{\rm{DEE}}+ 
    \left(\sum_{i \in A_1} d_{1i} {\bf z}_i - \sum_{i \in A_2} d_{1i} 
    \pi_{2i \mid 1}^{-1}  {\bf z}_i \right)\bm \phi^*$$

@@

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[size=custom,width=120,height=72,scale=1.0]{beamerposter}
\usetheme{gemini}
\usecolortheme{gemini}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{bm, ulem}
\pgfplotsset{compat=1.14}
\usepackage{anyfontsize}
\usepackage[backend=biber, style=bwl-FU]{biblatex}
\addbibresource{poster.bib}

@@

    In classical two-phase sampling, one first selects a sample $A_1$ from a
    finite population $U$ of size $N$, and observes $({\bf X}_i)_{i = 1}^{n_1}$.
    Then one selects a sample $A_2$ from $A_1$ and observes 
    $({\bf X}_i, Y_i)_{i = 1}^{n_2}$. We take the
    framework of two-phase sampling and view data integration as specific case
    of observing a variable of interest $Y$ within a single data set while we
    also observe common covariates $({\bf X}_i)$ between both the data set with
    $Y$ as well as an outside auxiliary sample. \sout{This is an important practical
    problem \cite{yang2020statistical}, 
    \cite{dagdoug2023model}.} We focus on the case:

@@

    \begin{itemize}
      \item In a seminal paper, \cite{deville1992calibration} generalized the
        regression estimator to other loss functions besides squared-error loss
        for a sample $A$ with auxiliary information about $X$. Their generalized
        loss function minimizes,

@@

  %\begin{theorem}[Design Consistency]\label{thm:dc1}
   \sout{Let $\bm \lambda^*$ be the probability limit of $\hat{\bm \lambda}$,
    where $\hat{\bm \lambda}$ are the corresponding Lagrange multipliers from
    Equation~\ref{eq:wmin}.}
    Under some regularity conditions, \sout{$\bm \lambda^* = ({\bf 0}^T, 1)^T$} and

    $$\hat Y_{\rm{DCE}} = \hat Y_\ell + O_p(N / n_2), $$

@@

    $$\hat Y_{\ell} = \hat Y_{\rm{DEE}}+ 
    \left(\sum_{i \in A_1} d_{1i} {\bf z}_i - \sum_{i \in A_2} d_{1i} 
    \pi_{2i \mid 1}^{-1}  {\bf z}_i \right)\bm \phi^*$$

@@

%\textcolor{red}{The linearization expression does not involve $\blambda^*$. }
\end{column}
